`r title`

### 2018-06-14 lib/report.Rmd
progress
starting the reboot

```{r by_incident_type_table, fig.align = 'left'}
by_incident_type_table
```

@@

```{r race_pct_plot}
race_pct_plot
```

```{r reason_for_stop_top_20_plot}
reason_for_stop_top_20_plot
```

```{r search_types_plot}
search_types_plot
```

@@

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
predicated_contraband_found_by_race_plot
if (exists("predicated_contraband_drugs_by_race_plot")) {
  predicated_contraband_drugs_by_race_plot
}
if (exists("predicated_contraband_weapons_by_race_plot")) {
  predicated_contraband_weapons_by_race_plot
}
```

```{r outcome_by_race_plot, fig.height = 10}
outcome_by_race_plot
```

@@

```{r loading_problems_count_table}
loading_problems_count_table
```

```{r loading_problems_random_sample_sorted_table}
loading_problems_random_sample_sorted_table
```

@@

```{r missing_columns_added_table}
missing_columns_added_table
```

>>>>

```{r by_type_table, fig.align = 'left'}
by_type_table
```

@@

```{r race_pct_plot}
display_if_exists("race_pct_plot")
```

```{r reason_for_stop_top_20_plot, fig.height = 15, fig.width = 10}
display_if_exists("reason_for_stop_top_20_plot")
```

```{r search_types_plot}
display_if_exists("search_types_plot")
```

@@

```{r plot_props_by_race}
display_if_exists("search_conducted_by_race_plot")
display_if_exists("contraband_found_by_race_plot")
display_if_exists("predicated_contraband_found_by_race_plot")
display_if_exists("predicated_contraband_drugs_by_race_plot")
display_if_exists("predicated_contraband_weapons_by_race_plot")
```

```{r outcome_by_race_plot, fig.height = 10}
display_if_exists("outcome_by_race_plot")
```

@@

```{r loading_problems_count_table}
display_if_exists("loading_problems_count_table")
```

```{r loading_problems_random_sample_sorted_table}
display_if_exists("loading_problems_random_sample_sorted_table")
```

@@
